Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-13 thesis/latex/thesis.tex
Thesis: spellcheck

\listoftables % Prints the list of tables
\newpage

@@

\subsection{Why do cells need motor transport?}
Cells are organized, heretogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
%%   \label{fig:diffusion_vs_dynein}
%% \end{figure}

@@

\subsection{Dynein structure}
As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.

@@

\section{Model overview}
The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell. In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation. Creating such a model is a balance between accuracy and computational efficiency. The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time. Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be infeasibly computationally expensive to simulate a dynein step. Thus, many approximations are made about dynein to simplify the simulation.\\

@@

How this system is used to generate data is covered later in the section. In brief, this system is then converted into a computer program. A technique known as Brownian dynamics, described below, is used by the program to evolve the model through time. Models are started in one state and evolved, occasionally transitioning from one state to another. The positions of each domain in time are stored as data. Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occured. Thus long simulations can be used to find the stepping behavior of a model.\\

@@

\subsection{Two-state model}
According to the Cianfrocco model, dynein takes on a total of eight states during a single step. Many of these states are conformationally very similar, eg the ADP- vs apo-bound or ATP- vs ADP-bound. Others involve quick transitions, eg from the just-MT-bound state to the post-powerstroke state. The transitions which take the most time according to reaction rate calculations are MT-binding and MT-release \cite{sarlahmodel}. Thus, these two states are taken to be the most important, and the Cianfrocco model is approximated by transitioning between these two states.\\

@@

\subsection{Binding to microtubule}
The model ``steps'' whenever an MTBD diffuses near the microtubule. \textit{In vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm. Thus, all dynein steps should be multiples of $8$nm. This model ignores this requirement and allows stepping to occur at any length. The assumption is that \textit{in vivo} dynein takes 8nm steps because it is tuned to take 8nm steps, not because it drags along the microtubule searching for a binding site. Thus the 8nm step length should be reproduced by the model even if stepping is allowed anywhere.\\

@@

The goal is to express angular velocities $\dot{\theta}_{bb}, \dot{\theta}_{bb}, \dot{\theta}_{bb}$ and $\dot{\theta}_{bb}$ in terms of known quantities. To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner. A subset of the equations are shown here:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\theta_{bb})\dot{\theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\theta_{bm})\dot{\theta}_{bm}
  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\theta_{fm})\dot{\theta}_{fm} \\
  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\theta_{fb})\dot{\theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\theta_{bb})\dot{\theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\theta_{bm})\dot{\theta}_{bm}
  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\theta_{fm})\dot{\theta}_{fm} \\
  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\theta_{fb})\dot{\theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}
%
Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:

@@

These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to new equations, some of which are shown here:

@@

This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, eg $\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$. These motion equations are further described in (\ref{sec:AppendixOneboundEquations}).\\

@@

              t += dt
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet}{Code snippet of Euler's method to update the positions of the onebound model simultaneously.}
  \label{snip:euler-code-snippet}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      def set_onebound_restoring_forces():
          T = cm*(nma - nma_eq);
          f1 = T/Ls;
          f2 = T/Lt;
          f1x = f1 * sin(bba);
          f1y = f1 * -cos(bba);
          f2x = f2 * sin(bma);
          f2y = f2 * -cos(bma);
          f.bbx += f1x;
          f.bby += f1y;
          f.tx  += f2x;
          f.ty  += f2y;
          f.bmx += -(f1x + f2x); // equal and opposite forces
          f.bmy += -(f1y + f2y);
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of restoring force calculation for near motor domain displacement.}{Torque is calculated the near motor's angular displacement from equilibrium. This is converted to force exerted on adjacent domains. Finally, the equal and opposite force is exerted on the near motor domain.}
  \label{snip:transition-rate-snippet}
\end{figure}

@@

where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the cartesian displacement of each domain $n$ due to the nudge. This test is powerful since it links the force-calculation system of either model to the energy calculation system. Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain. Having the force system and energy system calculate the same results indicates that they are both likely correct.\\

@@

%% \section{Validating model}
%% The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem. Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time. This is evidence that both the forces and velocities of the model are properly calculated. Grossly inncorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy. The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
  \end{tabular}
  \caption{Parameters used in processive simulations in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
  \label{table:thesis-parameters}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
  \caption{Near and far binding domains over the course of several microseconds of simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-trajectory}
\end{figure}

@@

\section{Model step size is highly variant}
Figure \ref{fig:final-histograms}.a shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}. This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Model vs experimental step sizes. \textbf{a.)} Step sizes model took at parameters in \ref{table:thesis-parameters}. \textbf{b.)} Experimental stepping behavior of dynein \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

Figure \ref{fig:final-histograms}.a shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$. This is a very important result, since it indicates that the model is capable of taking a varied step size. This behavior is characteristic of dynein, and hence very important to reproduce.\\

The preference for $<5nm$ steps is very un-dynein-like. One explanation is that steps may be defined differently between experimental and modeled dynein. In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram. This may not be how the experiment in \ref{fig:final-histograms}.b records steps. Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely. A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out. This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\

@@

Comparing the simulation results in \ref{fig:final-histograms}.a with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein. However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein. It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically. Lowering the binding rate may even out the histogram and prevent instant rebinding. It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm. Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\

@@

Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps. Kinesin, unlike dynein, conducts all of its chemistry directly on its foot. This translates to effectively having two fewer joints than dynein. Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism. The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge. This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics. If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating. This result would show that the differences betwen kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants. This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\

@@

\textbf{Onebound tests}
\begin{itemize}
\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths. Also checks that all angular velocities are zero. This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or cartesian) without forces.
\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths. Also check that all velocities are zero. This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that cartesian x-velocities are positive and y-velocities are zero. Verifies that the cartesian velocities have the expected sign.
\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all cartesian velocities are zero. Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite. Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
\end{itemize}
*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\

>>>>

%% \listoftables % Prints the list of tables
\newpage

@@

\subsection{Why do cells need motor transport?}
Cells are organized, heterogenous structures which respond quickly to their environments. This means that cells require a mechanism for rapidly moving components to precise locations within the cell. This can be a challenge, since cells are fairly large compared to the proteins which compose them. A human fibroblast cell has a volume of roughly 2000 $\mu m^3$\cite{fibroblastvolume}, corresponding to roughly $8 \mu m$ in diameter. In comparison, human hemoglobin has a diameter of roughly $5 nm$ (PDB id 5ME2), a $10^3$ factor difference in size.\\

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
%%   \caption{Passive diffusion vs motor transport rate}{Plot comparing the diffusion rate of a 140kD protein with a diffusion constant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
%%   \label{fig:diffusion_vs_dynein}
%% \end{figure}

@@

\subsection{Dynein structure}
As shown in the crystal structure in Figure \ref{fig:pdb-motm-dynein}, a dynein motor is a fusion of two identical subunits, or monomers, each with binding, stalk, motor and tail subdomains. Each of these subunits has a unique purpose for the motor.\\

@@

\section{Model overview}
The model constructed in this thesis is meant to accurately approximate how a protein with dynein's structure which underwent the conformational changes described in the Cianfrocco model \ref{sec:cianfrocco-model} would behave in a cell. In order to be compared to experiment, the model should output spatial information about dynein's rough conformation at all times during the simulation. Creating such a model is a balance between accuracy and computational efficiency. The model must be complex enough to correspond well to dynein, but not be so complex that it cannot be simulated in a reasonable amount of time. Molecular dynamics, a technique which simulates the individual amino acids in a protein, would be highly accurate, but would be prohibitively expensive to simulate a dynein step. Thus, many approximations are made about dynein to simplify the simulation.\\

@@

How this system is used to generate data is covered later in the section. In brief, this system is then converted into a computer program. A technique known as Brownian dynamics, described below, is used by the program to evolve the model through time. Models are started in one state and evolved, occasionally transitioning from one state to another. The positions of each domain in time are stored as data. Each time a model transitions from onebound to bothbound, the model registers a ``step'' having occurred. Thus long simulations can be used to find the stepping behavior of a model.\\

@@

\subsection{Two-state model}
According to the Cianfrocco model, dynein takes on a total of eight states during a single step. Many of these states are conformationally very similar, e.g. the ADP- vs apo-bound or ATP- vs ADP-bound. Others involve quick transitions, e.g. from the just-MT-bound state to the post-powerstroke state. The transitions which take the most time according to reaction rate calculations are MT-binding and MT-release \cite{sarlahmodel}. Thus, these two states are taken to be the most important, and the Cianfrocco model is approximated by transitioning between these two states.\\

@@

\subsection{Binding to microtubule}
The model ``steps'' whenever an MTBD diffuses near the microtubule. \textit{in vivo}, dynein binds to a site on the $\alpha-\beta$ tubulin polymer microtubule which repeats roughly every 8nm. Thus, all dynein steps should be multiples of $8$nm. This model ignores this requirement and allows stepping to occur at any length. The assumption is that \textit{in vivo} dynein takes 8nm steps because it is tuned to take 8nm steps, not because it drags along the microtubule searching for a binding site. Thus the 8nm step length should be reproduced by the model even if stepping is allowed anywhere.\\

@@

The goal is to express angular velocities $\dot{\theta}_{bb}, \dot{\theta}_{bb}, \dot{\theta}_{bb}$ and $\dot{\theta}_{bb}$ in terms of known quantities. To begin, the Cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner. A subset of the equations are shown here:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\theta_{bb})\dot{\theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\theta_{bm})\dot{\theta}_{bm}
  %% \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\theta_{fm})\dot{\theta}_{fm} \\
  %% \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\theta_{fb})\dot{\theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\theta_{bb})\dot{\theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\theta_{bm})\dot{\theta}_{bm}
  %% \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\theta_{fm})\dot{\theta}_{fm} \\
  %% \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\theta_{fb})\dot{\theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}
%
Another way to express these Cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:

@@

These two sets of equations, Cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to new equations, some of which are shown here:

@@

This matrix is then solved using the Mathematica computer algebra system, resulting in a set of motion equations which describe the model's trajectory over time, e.g. $\dot{\theta_{bm}}(\theta_{bb}, \theta_{bm}, \theta_{um}, \theta_{ub})$. These motion equations are further described in (\ref{sec:AppendixOneboundEquations}).\\

@@

              t += dt
    \end{lstlisting}
  \end{tabular}
  \caption{Euler's method code snippet.}{This code calculates domain velocities for onebound dynein and uses them to find position displacements. These values are stored in temporary variables first, then updated all at once.}
  \label{snip:euler-code-snippet}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      def set_onebound_restoring_forces():
          T = cm*(nma - nma_eq);
          f1 = T/Ls;
          f2 = T/Lt;
          f1x = f1 * sin(bba);
          f1y = f1 * -cos(bba);
          f2x = f2 * sin(bma);
          f2y = f2 * -cos(bma);
          f.bbx += f1x;
          f.bby += f1y;
          f.tx  += f2x;
          f.ty  += f2y;
          f.bmx += -(f1x + f2x); // equal and opposite forces
          f.bmy += -(f1y + f2y);
    \end{lstlisting}
  \end{tabular}
  \caption{Code snippet of restoring force calculation.}{Torque is calculated the near motor's angular displacement from equilibrium. This is converted to force exerted on adjacent domains. Finally, the equal and opposite force is exerted on the near motor domain.}
  \label{snip:transition-rate-snippet}
\end{figure}

@@

where $\theta_{nudge}$ was the angular nudge applied, $F_n$ the net force on domain $n$ and $\vec{r}_{n,nudge}$ the Cartesian displacement of each domain $n$ due to the nudge. This test is powerful since it links the force-calculation system of either model to the energy calculation system. Energy is calculated by looking at displacements of angles from equilibrium, whereas forces are calculated using displacement of angles from equilibrium, but also orientation and position of each domain. Having the force system and energy system calculate the same results indicates that they are both likely correct.\\

@@

%% \section{Validating model}
%% The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem. Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over a long time. This is evidence that both the forces and velocities of the model are properly calculated. Grossly incorrect velocity or force calculations would lead to an incorrect occupation distrobution of angles, and hence an incorrect average energy. The model's force calculations are further validated in Section \ref{sec:conformational-tests}, and energy conservation is validated in Section \ref{sec:energy-conservation}.\\

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    $k_{b}$ & $k_{ub}$ & $c_b$ &  $c_m$ & $c_t$ & dt\\\hline
    $10^{18} s^{-1}$ & $10^{20} s^{-1}$ & $2.0\Delta G_{ATP}$ & $2.0\Delta G_{ATP}$ & $1.0\Delta G_{ATP}$ & $10^{-10}s$\\ \hline
  \end{tabular}
  \caption{Parameters used in processive simulations.}{These parameters cause processive stepping in the dynein model, as shown in Figures \ref{fig:stepping-trajectory} and \ref{fig:final-histograms}.}
  \label{table:thesis-parameters}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../../plots/trajectory-plot_thesis}
  \caption{Dynein simulation displays processive stepping.}{Near and far binding domain x and y projections over the course of several microseconds of simulation. The blue foot corresponds to the ``near'' dimer closer to the viewer, and the red to the far dimer. Top: x-projection of binding domains over time. The motor steps roughly 50nm in 10 $\mu s$. Middle: cartoon depictions of the model during simulation. In the cartoons the blue foot's position on the x-axis corresponds to the time axis on the top and bottom plots. That is, the first cartoon corresponds to dynein at roughly 1 $\mu s$. The first cartoon corresponds to a bothbound model, and the second cartoon corresponds to a onebound model. Bottom: y-projection of binding domains over time. Notice that only one binding domain is above 0nm at any time.}
  \label{fig:stepping-trajectory}
\end{figure}

@@

\section{Model step size is highly variant}
Figure \ref{fig:final-histograms} shows the stepping pattern of the model at the parameters shown in Table \ref{table:thesis-parameters}. This simulation was run over a much longer time period, and hence shows much more significant information on the model's stepping behavior.\\

\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{../../plots/stepping_length_histogram_thesis}%%
    \includegraphics[width=0.5\textwidth]{../../figures/weihong-step-size.pdf}
    \caption{Stepping distribution of processive model and experimental dynein.}{Left: step sizes generated by model. Note the model can generate 25nm steps, but has a high preference for <5nm steps. Also note that no backward steps are generated by the model. Simulation run at conditions in \ref{table:thesis-parameters}. Right: Experimental stepping distribution of dynein, from \cite{weihongpaper}.}
    \label{fig:final-histograms}
\end{figure}

Figure \ref{fig:final-histograms} shows the model has a strong preference for $<5nm$ steps, but is capable of generating steps up to $25nm$ in length, with a fairly even distribution of step frequency between $5$ and $25nm$. This is a very important result, since it indicates that the model is capable of taking a varied step size. This behavior is characteristic of dynein, and hence very important to reproduce.\\

The preference for $<5nm$ steps is very un-dynein-like. One explanation is that steps may be defined differently between experimental and modeled dynein. In the simulation, every state transition where the motor unbinds from the microtubule is considered a step and plotted on the stepping histogram. This may not be how the experiment in \ref{fig:final-histograms} records steps. Another possibility is that the binding rate used for these simulations is far too high, and thus, immediate rebinding is very likely. A solution would thus be to lower the microtubule binding rate and see if the stepping histogram would level out. This may help, but may not, since lowering the binding rate would affect all binding probabilities, not just immediate rebindings.\\

@@

Comparing the simulation results in \ref{fig:final-histograms} with the experimental results in \ref{fig:final-histograms}.b, it is clear that the model is still far from experimental dynein. However, this is not indicative of a failure of the model, since the simulation parameters have not yet been tuned to dynein. It is very possible that changing the binding rate, unbinding rate and spring constants will change the stepping behavior of the model dramatically. Lowering the binding rate may even out the histogram and prevent instant rebinding. It may also allow the model to diffuse along the microtubule longer, generating longer steps than 25nm. Another issue is the lack of backwards steps, which may also be solved by altering the spring constants.\\

@@

Another very interesting simulation which could be run could help answer the open question of why kinesin and dynein, though using similar mechanisms, produce such different steps. Kinesin, unlike dynein, conducts all of its chemistry directly on its foot. This translates to effectively having two fewer joints than dynein. Kinesin's stroke is believed to involves a similar foot unbinding, kicking forward, rebinding, then lurching the motor forward mechanism. The dynein model could be used to construct a very rough model of kinesin by shrinking the tail linkers and increasing the motor domain spring constant $c_m$ high enough to simulate a rigid hinge. This model could then be reduced to the size of kinesin, given the proper equilibrium angles, and simulated with Brownian dynamics. If this new model even roughly manages to mimic experimental kinesin stepping,that would be fascinating. This result would show that the differences between kinesin and dynein can be explained exclusively through the values of spring constants $c_t$, $c_m$, $c_b$, lengths $L_s$ and $L_t$, equilibrium angles and un/binding constants. This would mean the differences between the two motors are primarily due to the conformational angles the motors take with the microtubule and between their own domains, not because of differences in their mechanism.\\

@@

\textbf{Onebound tests}
\begin{itemize}
\item \textbf{Onebound:} \textit{Upwards line conformation with no forces.} Check that all domain x-values are zero$^*$ and all y-values are the proper addition of $L_s$ and $L_t$ lengths. Also checks that all angular velocities are zero. This test verifies that the angle scheme is defined properly, that the model can handle straight lines without generating NaNs and that there are no velocities (angular or Cartesian) without forces.
\item \textbf{Onebound:} \textit{Horizontal line conformation with no forces.} Check that all domain y-values are zero and all x-values are the proper addition of $L_s$ and $L_t$ lengths. Also check that all velocities are zero. This test double-verifies that the coordinate system behaves as expected and that velocities are zero in the absence of forces.
\item \textbf{Onebound:} \textit{Upwards line conformation with +x forces} Check that Cartesian x-velocities are positive and y-velocities are zero. Verifies that the Cartesian velocities have the expected sign.
\item \textbf{Onebound:} \textit{Upwards line conformation with +y forces} Check that all Cartesian velocities are zero. Verifies that upwards forces in an already-vertical stalk have no effect on velocity.
  \item \textbf{Onebound:} \textit{Prepowerstroke opposing internal/brownian forces} Check that, for two onebound models, one with +x spring forces and no Brownian forces and the other with -x Brownian forces and no spring forces, that the velocities of each unbound domain are equal and opposite. Verifies that equal Brownian and internal forces have the same magnitude and direction of effect on velocities.
\end{itemize}
*: checks for equality are within a margin of error of $\epsilon = 1e^{-5}$.\\
